%%%%%%%%%%%%%%%%%
% This is an sample CV template created using maltacv.cls
% (May 2020) written by Riccardo Mancini, based on the 
% AltaCV template by LianTze Lim (liantze@gmail.com).
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

\documentclass[10pt,letter,ragged2e]{maltacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the font if you want to
% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage[default]{lato}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif

\usepackage{setspace}

\usepackage{mathpazo}
\usepackage{textcomp}
\usepackage{multicol}

% Color schemes:
% raisinblack_flame
% darkpurple_princetonorange
% blue_claret
% eerieblack_eggplant
% outerspace_forestgreen   
% raisinblack_midnightgreen
% teal_brown
% indigo
% blue
% violet
% you can set your custom colors with:
% \definecolor{AccentBody}{HTML}{002642}
% \definecolor{Primary}{HTML}{840032}
% \colorlet{primary}{Primary}
% \colorlet{accent_body}{AccentBody}

% this is my favourite but change it as you like
\setcolorscheme{raisinblack_flame}
\setlength\multicolsep{0pt}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}

%% sample.bib contains your publications
%% NOT SUPPORTED YET
% \addbibresource{sample.bib}

\name{George Dill}
\firstname{George}
\familyname{Dill}

\begin{document}
\tagline{Software Engineer}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{george.a.dill@gmail.com}
  % \birthday{25\textsuperscript{th} Dec 0}
  % \homepage{www.homepage.com/}
  % \twitter{@twitterhandle}
  \linkedin{georgedill}
  \github{kimjongdill}
  \phone{(773) 240 6809}
  % \mailaddress{lorem ipsum, dolor, sit, AM, 57846}
  \location{Chicago, IL}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
  % \orcid{orcid.org/0000-0000-0000-0000}
}

\makecvheader

\cvsection{Skills}
\begin{center}
  \begin{multicols}{5} % adjust #cols as needed
    \cvlistitem{JavaScript}{Node, React}
    \cvlistitem{C\#}{Dotnet MVC, EF}
    \cvlistitem{Java}{Spring Boot}
    \cvlistitem{DevOps}{K8s, Docker, CI/CD}
  \end{multicols}
\end{center}

% put Experience before Education if you are no longer a student
\cvsection{Experience}
\cvcompany{Nvisia}{Chicago, IL}
\cvtitle{Technical Lead}{Nov 2021 -- Present}
\cvtitle{Software Engineer}{Feb 2020 -- Nov 2021}
\smallskip
\textit{Nvisia is a mid-size software consultancy developing business solutions for the enterprise communities in Chicago, IL and Milwaukee, WI. I am working 
    on engineering teams at Echo Global Logistics, a freight brokerage nearing \$4 Billion in revenue in 2021.}\par
\smallskip
\begin{itemize}
  \item Enabled continuous deployment and reduced build time by 20 minutes of Echo's Transportation Management System single page app 
    by porting it to a microfrontend architecture. 
  \item Designed Echo's first fully automated cloud deployment for a single page application using 
    AWS cloud objects including S3, Cloudfront, Cloudfront Functions, Certificate Manager, and Terraform. 
  \item Maintained a portable local development environment using Skaffold for 
    automated deployments to K8s, Kustomize for managing environment specific 
    variables, and lightweight mocks using node.JS and fastify. 
  \item Programmed an event-driven data persistence layer using the CQRS pattern in 
    C\# with commands consumed from rabbitMQ, an MS-SQL write store and 
    Elasticsearch read store.
\end{itemize}
\cvkeyword{React.JS, Node.JS, C\#, Dotnet Core, Dotnet MVC, MS-SQL, AWS, Terraform}
\divider

\cvcompany{University of Illinois at Chicago}{Chicago, IL}
\cvtitle{Research Assistant}{May 2019 -- Dec 2019}
\smallskip
\begin{itemize}
  \item Refactored the delegation system described in \href{https://www.cs.uic.edu/~jakob/papers/sosp17_techrep_draft.pdf}{"ffwd: delegation is (much) faster than you think"} to handle asynchronous jobs.
  \item Using the Intel developers guide and modeling the cache hierarchy, increased throughput of "ffwd" on microbenchmarks by 18\%
  \item Wrote BASH scripts to run trials, parsed output with Awk and Sed, and displayed results with Gnuplot.
  \item Published results as a Masters Thesis: \href{https://indigo.uic.edu/articles/thesis/Asynchronous_Delegation_and_Applications/12481784}{Asynchronous Delegation and its Applications}. 
\end{itemize}
\cvkeyword{C, C++, Delegation, X86-64, Intel, BASH}

\divider

\cvcompany{Amazon}{Seattle, WA}
\cvtitle{Software Engineer Intern}{Summer 2018}
\smallskip
\begin{itemize}
  \item Refactored a Java application to pass data in key-value pairs through a series of micro-services implemented on AWS lambda, SQS, and EC2.
\end{itemize}
\cvkeyword{Java, AWS}
%Projects
% - Newspaper E-Ink Display
% - Remote Control Air Conditioner

\divider

\cvsection{Certifications and Awards}
\medskip
\begin{itemize}
  \item AWS Certified Solutions Architect
  \item Disciplined Agile Senior Scrum Master
  \item Excellent TA Award
  \item Winner - Built Worlds Hackathon 2017
\end{itemize}

\medskip
\cvsection{Education}
\medskip
\begin{multicols}{2}

  \cvuniversity{M.Sc. Computer Science}{University of Illinois at Chicago}{December 2019}{}% last param is location
  % this helps if columns are not the same
  \vfill\null
  \columnbreak

  \cvuniversity{B.Sc. Civil Engineering}{Purdue University}{May 2008}{West Lafayette, IN}
  \vfill\null

\end{multicols}


\end{document}